
\textbf{Steps of Normalization:}
\begin{itemize}
	\item [\textbf{Tokenization}] Turning text into words.
	\subitem \textbf{Example:} My name is quin and I live in Georgia.

	This contains nine tokens or words.
	\item [\textbf{Lemmatization}] Reducing a collection of words to their root meaning
	\subitem \textbf{Example:} My name is quin and I am living in Georgia. I lived in Georgia for a while.

	Living and lived will be reduced to live.
	\item [\textbf{Stemming}] Close to Lemmatization, with Stemming you're taking away the suffixes.
	\subitem \textbf{Example:} My name is quin and I am living in Georgia. I lived in Georgia for a while.

	Living and lived will be reduced to liv.
	\item [\textbf{Sentence Segmentation}] Breaking up the text with the delimiters of . , ! or ?
	\subitem \textbf{Example:} My name is quin and I am living in Georgia. I lived in Georgia for a while. I like living here.
		\begin{itemize}
			\item [\textbf{Sentence One}] My name is quin and I am living in Georgia.
			\item [\textbf{Sentence Two}] I lived in Georgia for a while.
			\item [\textbf{Sentence Three}] I like living here.
		\end{itemize}
	\item [\textbf{Spelling Correction}] Checking for spelling mistakes.
	\subitem \textbf{Example:} My name is quin afd I live in Georgia.

	The word afd should be and.
	\item [\textbf{Non-Standerd Words}] Phone numbers, emails, dates, etc.
	\subitem \textbf{Example:} My name is quin and my phone number is  704-470-7036, and email is qlyleswo@student.kennesaw.edu.
		\begin{itemize}
			\item [\textbf{Phone Number}] 704-470-7036
			\item [\textbf{Email}] qlyleswo@student.kennesaw.edu
	\end{itemize}

\end{itemize}